title

### 2022-03-14 _paper.rmd
partially working .sty (z_sty_reprex/)

---
title: "Exploring Local Explanations of Nonlinear Models Using Animated Linear Projections"
shorttitle: Cheem
keywords:
  - R
  - XAI
  - explanable artificial intelligence
  - black-box models
  - local explanations
  - grand tour
  - manual tour
  - radial tour
author:
- Nicholas Spyrison 
#^[Monash University, nicholas.spyrison@monash.edu, ORCiD: 0000-0002-8417-0212]
- Dianne Cook
- Kimbal Marriott
#^[ORCiD: 0000-0002-9813-0377]
  #- name: "Nicholas Spyrison"
  #   affiliation: Monash University
  #   address: |
  #     | ORCiD: 0000-0002-8417-0212
  #   email: \email{nicholas.spyrison@monash.edu}
  #   orcid: 0000-0002-8417-0212
  #- name: "Dianne Cook"
  #   affiliation: Monash University
  #   address: |
  #     | ORCiD: 000-0002-3813-7155
  #   orcid: 000-0002-3813-7155
  #- name: "Kimbal Marriott"
  #   affiliation: Monash University
  #   address: |
  #     | ORCiD: 0000-0002-9813-0377
  #   orcid: 0000-0002-9813-0377
abstract: |
 The increased predictive power of nonlinear models comes at the cost of interpretability of its terms.  This trade-off has led to the emergence of eXplainable AI (XAI). XAI attempts to shed light on how models use predictors to arrive at a prediction with _local explanations_, a point estimate of the linear feature importance in the vicinity of one instance. These can be considered linear projections and can be further explored to understand better the interactions between features used to make predictions across the predictive model surface. Here we describe interactive linear interpolation used for exploration at any instance and illustrate with examples with categorical (penguin species, chocolate types) and quantitative (soccer/football salaries, house prices) output. The methods are implemented in the __R__ package __cheem__, available on CRAN.
#documentclass: jmlr2e
#classoption: article
output:
  ## pdf_document: requires \ref{} 
  pdf_document:
  ## bookdown::pdf_document2: allows \@ref(), but doesn't add authors....
  #bookdown::pdf_document2:
    #includes:
    #  in_header: template/jmlr2e.sty
    keep_tex: true
    toc: false
    number_sections: yes
    fig_caption: yes
bibliography: cheem_paper.bib
editor_options:
  chunk_output_type: console
urlcolor: blue
linkcolor: red
header-includes:
  - \usepackage{setspace} ## for title page spacing
  - \usepackage{hyperref} ## for all sorts of linking
---

>>>>

---
title: "Exploring Local Explanations of Nonlinear Models Using Animated Linear Projections"
shorttitle: Cheem
keywords:
  - R
  - XAI
  - explanable artificial intelligence
  - black-box models
  - local explanations
  - grand tour
  - manual tour
  - radial tour
author:
- Nicholas Spyrison 
#^[Monash University, nicholas.spyrison@monash.edu, ORCiD: 0000-0002-8417-0212]
- Dianne Cook
#^[ORCiD: 000-0002-3813-7155]
- Kimbal Marriott
#^[ORCiD: 0000-0002-9813-0377]
  #- name: "Nicholas Spyrison"
  #   affiliation: Monash University
  #   address: |
  #     | ORCiD: 0000-0002-8417-0212
  #   email: \email{nicholas.spyrison@monash.edu}
  #   orcid: 0000-0002-8417-0212
  #- name: "Dianne Cook"
  #   affiliation: Monash University
  #   address: |
  #     | ORCiD: 000-0002-3813-7155
  #   orcid: 000-0002-3813-7155
  #- name: "Kimbal Marriott"
  #   affiliation: Monash University
  #   address: |
  #     | ORCiD: 0000-0002-9813-0377
  #   orcid: 0000-0002-9813-0377
abstract: |
 The increased predictive power of nonlinear models comes at the cost of interpretability of its terms.  This trade-off has led to the emergence of eXplainable AI (XAI). XAI attempts to shed light on how models use predictors to arrive at a prediction with _local explanations_, a point estimate of the linear feature importance in the vicinity of one instance. These can be considered linear projections and can be further explored to understand better the interactions between features used to make predictions across the predictive model surface. Here we describe interactive linear interpolation used for exploration at any instance and illustrate with examples with categorical (penguin species, chocolate types) and quantitative (soccer/football salaries, house prices) output. The methods are implemented in the __R__ package __cheem__, available on CRAN.
#documentclass: jmlr2e
#classoption: article
output:
  ## pdf_document: requires \ref{} 
  pdf_document:
  ## bookdown::pdf_document2: allows \@ref(), but doesn't add authors....
  #bookdown::pdf_document2:
    #includes:
    #  in_header: template/jmlr2e.sty
    keep_tex: true
    toc: false
    number_sections: yes
    fig_caption: yes
bibliography: cheem_paper.bib
editor_options:
  chunk_output_type: console
urlcolor: blue
linkcolor: red
header-includes:
  - \usepackage{setspace} ## for title page spacing
  - \usepackage{hyperref} ## for all sorts of linking
---

### 2022-03-14 z_sty_reprex/sty_reprex.rmd
partially working .sty (z_sty_reprex/)

---
title: "title"
author: 
  - author
  - author2
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header:
        #- ../template/jmlr2e.sty ## Doesn't work
        #- tmp_jmlr.tex ## Doesn't work
        - mystyles.sty ## Works
---

@@

>>>>

---
title: "title"
author: 
  - author
  - author2
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header:
        - jmlr2e.sty ## Doesn't work
        #- mystyles.sty ## Works (trivial \usepackage{})
---

@@

# Attempts and notes

- Trivial sty files work (mystyles.sty)
- Trivial tex file didn't work.
- jmlr2e.sty doesn't work wholesale, hence:
- Changing to *.tex didn't work.
- Trying to pare back and to isolate the issue:
    - adding \makeatletter and \makeatother to change the order of operations handling @ in marco assignment. _partial success!!_
    - uncommenting .sty file, keeping an eye out for @ in macronames. 
    - \makeatletter and \makeatother at top and bottom is back to original error... (! LaTeX Error: Missing \begin{document}.); try changing back and forth
